\bf A Hierarchical Model for Heterogenous Reliability Field Data

### 2018-01-24 paper/m-lb-m-technometrics.tex
Enlarge legend for figure 5
small edits.

\section{Introduction}
\subsection{Motivation}
Consumers have an interest in accurate assessment of product reliability. Toward this end, there usually is a need for models that can accomodate common failure patterns and methods which can make the most of available data and properly account for uncertainty. Doing these things well enables good decision-making in matters related to product life, including purchase decisions and contingency planning.
%While computationally convenient, simple lifetime models can fail at each of these.

>>>>

\section{Introduction}
\subsection{Motivation}
Consumers have an interest in accurate assessment of product reliability}. Toward this end, there usually is a need for models that can accommodate common failure patterns and methods which can make the most of available data and properly account for uncertainty. Doing these things well enables good decision-making in matters related to product life, including purchase decisions and contingency planning.
%While computationally convenient, simple lifetime models can fail at each of these.
